---
title: "Wordflock"
author: "Charlie Bayne"
date: "12/11/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(twitteR)
library(wordcloud2)
library(tidyverse)
library(plotly)
`%!in%` = Negate(`%in%`)
```

## What is Wordflock?  

Wordflock is an app designed to visualize word usage information from a twitter user's tweet history in the form of a word cloud.  

The app has three main functions:  
1. Building a wordcloud from a desired users twitter handle.  
2. Comparing two twitter users to see the words that were most commonly shared.  
3. Comparing two twitter users to see the words that were shared on the same date.  


## Uses  

This app is mostly designed to be a fun visualization! It can be used to visualize the things that are the most important to a given twitter user (if you are willing to assume that the frequency a word is said correlates with its importance). 

It can also be used to loosely infer similarities and relationships between any two twitter users.  

## Details  

This app runs using R shiny and acesses twitter using the rtweet package.  

Obviously, some words (such as "a") are very common but not necessarily interesting. This app attempts to account for this by removing words that are in the list of the top100 most used words.  

For shared tweets, the word cloud is generated from the average number of time the word is mentioned between the two users. 


## Example  


```{r}
top100 = read.csv("www/Most_frequently_used_words.csv")
            tw = rtweet::get_timeline("realdonaldtrump",n = 1000)
            
            words = unlist(strsplit(tw$text, " ")) 
        
            df = as.data.frame(table(words)) %>% 
                dplyr::filter(words %!in% top100$Words)
        
            wordcloud2(df)
        
```

Here is an example of the word cloud produced when looking at the presidents tweets. Interestingly, some patterns seem to emerge.

## Thanks!  

Thanks for viewing and I hope you enjoy using Wordflock!  



